---
title: "Introduction to fixes"
author: "Yosuke Abe"
date: "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.Date(), '%B %d, %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to fixes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE,
  fig.width = 7,
  fig.height = 5,
  dpi = 150,
  eval = requireNamespace("fixest", quietly = TRUE)
)

library(fixes)
library(dplyr)
library(ggplot2)
```

## Introduction

The **fixes** package provides an easy-to-use toolkit for estimating and
visualizing difference-in-differences designs on panel data: event-study
curves via `event_study()`, aggregated ATT via `att()`, and basic two-way
fixed-effects DiD via `did()`. Every result has a base `plot()` method, so a
complete analysis is a two-line pipeline.

Estimation runs on the package's internal C++ fixed-effects OLS engine;
the `fixest` package is an optional dependency (used only in this vignette
for its example datasets and a few advanced specifications).

> **Upgrading from fixes < 1.0.0?** The old verb-style functions
> (`run_es()`, `calc_att()`, `run_did()`, `plot_es()`, ...) still work and
> return identical results, but are deprecated. This vignette uses the new
> noun-style API introduced in 1.0.0.

## Installation

Install the released version from CRAN:

```r
install.packages("fixes")
```

Or with **pak** (recommended for fast install):

```r
pak::pak("fixes")
```

To install the latest development version from GitHub:

```r
pak::pak("yo5uke/fixes")
```

## Minimal Example

Below is a basic example using the built-in `fixest::base_did` dataset,
running an event study, and visualizing the results.

```{r minimal-example}
# Load example data
df <- fixest::base_did

# Run the event study (supports multiple confidence levels)
es <- event_study(
  data       = df,
  outcome    = y,
  treatment  = treat,
  time       = period,
  timing     = 5,  # Treatment occurs at period 5 (universal timing)
  fe         = ~ id + period,
  cluster    = ~ id,
  baseline   = -1,
  interval   = 1,
  lead_range = 3,
  lag_range  = 3,
  conf_level = c(0.90, 0.95, 0.99)  # Multiple CIs supported!
)

# View results
head(es)
```

Because `timing = 5` is a scalar, `event_study()` recognizes a universal
(non-staggered) design automatically; when `timing` names a column of
adoption times, a staggered design is inferred instead.

## Visualizing Event Study Results

Results plot directly with `plot()`. You can switch between ribbon-style or
error bar CIs, select the displayed CI level, and customize appearance.

```{r plot-basic}
# Basic plot (default: ribbon, 95% CI)
plot(es)
```

```{r plot-errorbar}
# Plot with error bars and 99% CI
plot(es, type = "errorbar", ci_level = 0.99)
```

```{r plot-custom}
# Customize further with ggplot2
plot(es, type = "errorbar", ci_level = 0.9, theme_style = "classic") +
  scale_x_continuous(breaks = seq(-3, 3, by = 1)) +
  ggtitle("Event Study with 90% CI and Classic Theme")
```

For interactive exploration with hover tooltips (estimates, CIs, standard
errors, p-values), pass `interactive = TRUE` (requires the suggested
**plotly** package):

```r
plot(es, interactive = TRUE)
```

## Package Highlights

- **`event_study()`**:
    - Fast, one-step event study for panel data on an internal C++
      fixed-effects engine.
    - Six estimators behind one interface (`estimator =`): classic TWFE,
      Callaway & Sant'Anna, Sun & Abraham, Borusyak-Jaravel-Spiess,
      Wooldridge two-way Mundlak, and Deb et al. FLEX.
    - Automatic creation of lead/lag dummies relative to treatment, with
      staggered/universal timing inferred from `timing`.
    - Covariates, clustering, weights, and flexible baseline normalization.
    - Multiple confidence interval levels (e.g., 90%, 95%, 99%).
    - Handles irregular time panels via `time_transform`.

- **`att()`**: aggregated ATT — overall, by cohort, or by calendar time —
  for the CS and BJS estimators, with `broom::tidy()`/`glance()` methods.

- **`did()`**: single-coefficient TWFE DiD compatible with
  `modelsummary::modelsummary()`.

- **`plot()`**: every result class has a plot method — event-study curves,
  ATT point-range charts, ATT(g,t) heatmaps (`plot(att_gt(x))`), honest
  sensitivity plots, and contamination-weight heatmaps.

## Staggered adoption estimators

Standard TWFE event-study regressions can produce biased and sign-reversed
estimates under heterogeneous treatment effects when units adopt treatment at
different times (Callaway & Sant'Anna 2021; Sun & Abraham 2021; Borusyak,
Jaravel & Spiess 2024). **fixes** provides robust alternatives, all
accessible through the same `event_study()` interface via the `estimator`
argument.

We demonstrate three of them on `fixest::base_stagg`, a simulated
staggered-adoption panel with true ATT = 1 for all cohorts and horizons.

```{r stagg-data}
df_stagg <- fixest::base_stagg
# Mark never-treated units with NA (convention for all staggered estimators)
df_stagg$timing <- df_stagg$year_treated
df_stagg$timing[df_stagg$year_treated == 10000] <- NA
```

### Callaway & Sant'Anna (2021) — `estimator = "cs"`

Estimates a separate ATT(g,t) for every cohort-by-period cell, then aggregates
to an event-study curve using cohort-size weights.

```{r cs-est}
res_cs <- event_study(
  data          = df_stagg,
  outcome       = y,
  time          = year,
  timing        = timing,
  unit          = id,
  estimator     = "cs",
  control_group = "nevertreated"
)
plot(res_cs) + ggplot2::ggtitle("Callaway & Sant'Anna (2021)")
```

### Sun & Abraham (2021) — `estimator = "sa"`

Builds cohort x relative-time interactions and aggregates with cohort-share
weights. Numerically identical to `fixest::sunab()` (which the deprecated
`run_es(method = "sunab")` used directly).

```{r sa-est}
res_sa <- event_study(
  data      = df_stagg,
  outcome   = y,
  treatment = treated,
  time      = year,
  timing    = timing,
  unit      = id,
  fe        = ~ id + year,
  estimator = "sa",
  cluster   = ~ id
)
plot(res_sa) + ggplot2::ggtitle("Sun & Abraham (2021)")
```

### Borusyak, Jaravel & Spiess (2024) — `estimator = "bjs"`

Fits TWFE on untreated observations, imputes counterfactuals for treated units,
then averages by horizon.

```{r bjs-est}
res_bjs <- event_study(
  data      = df_stagg,
  outcome   = y,
  time      = year,
  timing    = timing,
  unit      = id,
  estimator = "bjs"
)
plot(res_bjs) + ggplot2::ggtitle("Borusyak, Jaravel & Spiess (2024)")
```

Under homogeneous treatment effects (as in this DGP), the estimators give
similar results, each recovering a post-treatment ATT close to the true
value of 1. Wooldridge's two-way Mundlak (`"twm"`) and the Deb et al. FLEX
estimator for repeated cross-sections (`"flex"`) round out the set.

### Aggregated ATT — `att()`

When you want a single number (or one per cohort / per period) instead of
the full curve:

```{r att-demo}
att(df_stagg, outcome = y, time = year, timing = timing, unit = id,
    estimator = "cs", aggregation = "simple")
```

---

## Bootstrap simultaneous confidence bands

### Pointwise vs. simultaneous CIs

Standard confidence intervals are **pointwise**: the 95% CI at each horizon
covers the true value with 95% probability, but the probability that *all*
intervals simultaneously cover their true values can be much lower when many
periods are plotted.

**Simultaneous** confidence bands (Callaway & Sant'Anna 2021, Corollary 1)
control the joint coverage probability. With probability at least 1 − α, the
entire event-study curve is contained within the simultaneous band. This is
especially important for parallel-trends pre-testing: a pre-trend test based
on simultaneous bands controls the family-wise error rate.

### Usage

Pass `bootstrap = TRUE` to `event_study()` together with the CS estimator.
The multiplier bootstrap (Algorithm 1 of Callaway & Sant'Anna 2021) is used.

```{r boot-demo, eval=FALSE}
# NOTE: boot_reps = 199 shown here for brevity; use 999 in practice
res_cs_boot <- event_study(
  data          = df_stagg,
  outcome       = y,
  time          = year,
  timing        = timing,
  unit          = id,
  estimator     = "cs",
  control_group = "nevertreated",
  bootstrap     = TRUE,
  boot_reps     = 199,
  boot_seed     = 42
)
# The lighter outer band is the simultaneous CI; the darker inner band is
# the standard pointwise CI.
plot(res_cs_boot, show_simultaneous = TRUE)
```

The simultaneous critical value ĉ and per-period simultaneous CI bounds are
stored in `attr(res_cs_boot, "bootstrap")`. The simultaneous band is always
at least as wide as the pointwise band, since the critical value
ĉ_{1-α} >= z_{1-α/2}.

---

## ATT(g,t) visualization

The CS estimator produces a separate ATT estimate for every (cohort g,
calendar period t) pair. Extract the full matrix with `att_gt()` and plot it.

### Heatmap

Tiles are filled by the ATT(g,t) estimate. Cells whose pointwise CI excludes
zero are marked with a filled dot (●); when bootstrap data are available,
simultaneously significant cells also receive an open diamond (◇).

```{r heatmap-demo}
plot(att_gt(res_cs), type = "heatmap")
```

The vertical dashed lines mark each cohort's treatment onset (t = g).

### Facet plot

One panel per cohort showing ATT over calendar time, with a pointwise CI
ribbon. Useful for inspecting heterogeneous dynamics across cohorts.

```{r facet-demo}
plot(att_gt(res_cs), type = "facet")
```

---

## Conclusion

The **fixes** package streamlines event study estimation and visualization for panel data researchers. With a minimal API, multiple CI support, and robust visualization, it accelerates the workflow for dynamic treatment effect analysis.

For further details and full argument documentation, see:

```r
?event_study
?att
?did
?plot.es_result
```

Happy analyzing!
